---
output: github_document
---

# ogbox
```{r,echo=FALSE,results=FALSE}
library(ogbox)
```

[![Build Status](https://travis-ci.org/oganm/ogbox.svg?branch=master)](https://travis-ci.org/oganm/ogbox)[![codecov.io](https://codecov.io/github/oganm/ogbox/coverage.svg?branch=master)](https://codecov.io/github/oganm/ogbox?branch=master)


A multi-purpose R package primarily for personal use

## Installation
```
devtools::install_github('oganm/ogbox')
```

## What's in the box?

There are many poorly documented functions here. Below are some examples separated
by category.


### Developer tools

`getVersion`, `setVersion` and `setDate` functions allow manipulation of DESCRIPTION files.
I use them for auto updating packages.

`forkCRAN` allows you to create a github repository for a current or older version of a cran package which can be followed up by `install_github` or `Remotes`
in your DESCRIPTION file if you really need an older version of a package or want to make some changes yourself

### List unpacking

Taken from [this](http://stackoverflow.com/questions/1826519/function-returning-more-than-one-value) github answer ages ago, this syntax

```{r}
list[a,b] = list(c(1,2,3),c(4,5,6))
a
b
```

allows unpacking of lists. These days `zeallot` package does that with %<-% operator.

### Remote code sourcing and data loading

* `sourceGithub` runs R scripts or specific lines of R scripts from github.
* `loadURL` and `loadGithub` loads remote rda files
* `readRDSGithub` reads an RDS file from github
* `getGithubFile`, also used by the functions above gets files from github.

### Gene Expression Omnibus tools

Didn't want to deal with S4 classes from bioconductor packages so there are a bunch of functions that deal with GEO datasets.

* `gsmFind` picks samples that match a regex from a dataset
* `whichGSE` finds the datasets that a sample belongs to
* `gsmDown` downloads cel files for microarray samples
* `gseDown` downloads all cel files for a microarray dataset
* `softDown` downloads softfile for an experiment
* `softParser` parses said soft file.
